Adaptive evolution with aneuploidy and mutation

### 2022-01-24 ms/ms.tex
small revisions

% TODO cite https://www.biorxiv.org/content/10.1101/2020.10.07.327759v1
% TODO cite Yang, F. et al. The fitness costs and benefits of trisomy of each Candida albicans chromosome. Genetics 218, 1–7 (2021). https://academic.oup.com/genetics/article/218/2/iyab056/6218773

@@

% FIG posterior
\begin{figure}[h!]
  \centering
\includegraphics[width=0.9\textwidth]{../figures/posterior.pdf}
  \caption{
  \textbf{Posterior distribution of single-locus model.}
On the diagonal, the posterior kernel distribution of each model parameter. 
Below the diagonal, joint posterior distribution of pairs of model parameters (dark purple and bright yellow for low and high density, respectively). Red markers and orange lines for the joint MAP estimate (which may differ from the marginal MAP, as the marginal distribution integrates over all other parameters).
} 
% TODO less y axis ticks
% more x axes ticks?
  \label{fig:posterior}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/dynamics.pdf}
  \caption{
  \textbf{Single-locus model posterior genotype frequency dynamics.} 
  The posterior predicted frequency of the four genotypes. Each of 20 curves is the average of 10,000 simulations using parameters drawn from the posterior distribution (\autoref{fig:posterior}).
  }
  \label{fig:ppc-plot}
  % TODO put legend inside figure - I think there is room in middle right
\end{figure}

@@

% Fig likelihood profile
\begin{figure}[p]
  \centering
  \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-A.pdf}      
      \label{fig:sensitivity-mutation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-B.pdf}      
      \label{fig:sensitivity-aneuploidy}
  \end{subfigure}
  \\
   \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-C.pdf}      
      \label{fig:sensitivity-anwt}
  \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-D.pdf}      
      \label{fig:sensitivity-anmt}
  \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-E.pdf}      
      \label{fig:sensitivity-eumt}
  \end{subfigure}
  \caption{
    \textbf{Likelihood profiles.} Sensitivity of the approximate likelihood, $\likelihood(\theta)$, of the single-locus model to changing a single parameter while the other parameters remain fixed at their MAP estimates. Dashed vertical line represents the MAP value.
  }
  % TODO add 10^-10, not 10^-2
  % TODO ylabel - L shouldn't have a subscript !, this was used only for the model without aneuploidy
  % TODO add more points in the peaks

  \label{fig:sensitivity}
\end{figure}

>>>>

% TODO cite https://www.biorxiv.org/content/10.1101/2020.10.07.327759v1
% TODO cite Yang, F. et al. The fitness costs and benefits of trisomy of each Candida albicans chromosome. Genetics 218, 1–7 (2021). https://academic.oup.com/genetics/article/218/2/iyab056/6218773
% cite: https://www.cell.com/developmental-cell/fulltext/S1534-5807(21)00562-1?_returnURL=https%3A%2F%2Flinkinghub.elsevier.com%2Fretrieve%2Fpii%2FS1534580721005621%3Fshowall%3Dtrue
% cite: https://www.cell.com/developmental-cell/fulltext/S1534-5807(21)00592-X?_returnURL=https%3A%2F%2Flinkinghub.elsevier.com%2Fretrieve%2Fpii%2FS153458072100592X%3Fshowall%3Dtrue

@@

% FIG posterior
\begin{figure}[h!]
  \centering
\includegraphics[width=0.9\textwidth]{../figures/posterior.pdf}
  \caption{
  \textbf{Posterior distribution of single-locus model.}
On the diagonal, the inferred posterior distribution of each model parameter. 
Below the diagonal, the inferred joint posterior distribution of pairs of model parameters (dark purple and bright yellow for low and high density, respectively). Red markers and orange lines for the joint MAP estimate (which may differ from the marginal MAP, as the marginal distribution integrates over all other parameters).
} 
  \label{fig:posterior}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
  \centering
\includegraphics[width=0.8\textwidth]{../figures/dynamics.pdf}
  \caption{
  \textbf{Posterior genotype frequency dynamics for the single-locus model.} 
  The posterior prediction for the frequencies of the four genotypes over time. Each of the 20 curves is the average of 10,000 simulations of the single-locus model using parameters drawn from the posterior distribution.
  }
  \label{fig:ppc-plot}
\end{figure}

@@

% Fig likelihood profile
\begin{figure}[p]
  \centering
  \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-A.pdf}      
      \label{fig:sensitivity-mutation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-B.pdf}      
      \label{fig:sensitivity-aneuploidy}
  \end{subfigure}
  \\
   \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-C.pdf}      
      \label{fig:sensitivity-anwt}
  \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-D.pdf}      
      \label{fig:sensitivity-anmt}
  \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \includegraphics[width=\textwidth]{../figures/sensitivity-E.pdf}      
      \label{fig:sensitivity-eumt}
  \end{subfigure}
  \caption{
    \textbf{Likelihood profiles.} Sensitivity of the approximate likelihood of the single-locus model, $\likelihood(\theta)$, to changing a single parameter while the other parameters remain fixed at their MAP estimates. Dashed vertical line represents the MAP value.
  }

  \label{fig:sensitivity}
  % TODO what defines the x range? is it the prior distribution range?
\end{figure}
